---
title: "DS3Goe"
author: "Abigail Cochran"
date: "8/12/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

First, I'll call the libraries that I may want to use for my analysis.
```{r}
#Call necessary libraries
library(datasets)
library(ggplot2)
library(tidyverse)
```

Then I'll download the data, and take a quick look.
```{r}
#Call the IRIS dataset
data(iris)

#Summarize the dataset.
summary(iris)
```

Great. Now let's figure something out. How about how the ratio of sepal length to width, and petal length to width differs across species. First, let's format the data as a dataframe.

```{r}
#Make Iris into a dataframe.
dfiris <- as.data.frame(iris)

#Take a quick look at data types
str(dfiris)
# All numerics and factors (for species), that's what we want.
```

Now let's manipulate the dataframe.

```{r}
# First get the ratio for sepals and petals per line, then group by species, then get the average ratios for each species.

dfirismut <- dfiris %>%
  mutate(sepal.ratio = Sepal.Length/Sepal.Width) %>%
  mutate(petal.ratio = Petal.Length/Petal.Width) %>%
  group_by(Species) %>%
  mutate(sepal.lw.ratio.avg = mean(sepal.ratio)) %>%
  mutate(petal.lw.ratio.avg = mean(petal.ratio))
```

This worked. I get what I want. The average sepal length/width raio is 1.470188 for setosa, 2.160402 for versicolor, and 2.230453 for virginica. The average petal length/width ratio is 6.908 for setosa, 3.242837 for versicolor, and 2.780662 for virginica. 

For sepals: virginica > versicolor > setosa. 

For petals: setosa > versicolor > verginica. 

This leads me to believe that these measurements might have an inverse relationsihp. Cool!
